\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-03-10 paper/forestecology.tex
Re-knit manuscript just in case

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{comp_bayes_lm_scbi}
\CommentTok{## Bayesian linear regression model parameters with a multivariate Normal likelihood. See ?comp_bayes_lm for details:}
\CommentTok{## }
\CommentTok{##   parameter_type           prior posterior}
\CommentTok{## 1 Inverse-Gamma on sigma^2 a_0   a_star   }
\CommentTok{## 2 Inverse-Gamma on sigma^2 b_0   b_star   }
\CommentTok{## 3 Multivariate t on beta   mu_0  mu_star  }
\CommentTok{## 4 Multivariate t on beta   V_0   V_star   }
\CommentTok{## }
\CommentTok{## Model formula:}
\CommentTok{## growth ~ sp + dbh + dbh * sp + acne * sp + acru * sp + amar * sp + astr * sp + caca * sp + caco * sp + cade * sp + cagl * sp + caovl * sp + cato * sp + ceca * sp + ceoc * sp + chvi * sp + cofl * sp + crpr * sp + crsp * sp + divi * sp + elum * sp + fagr * sp + fram * sp + frni * sp + frpe * sp + havi * sp + ilve * sp + juci * sp + juni * sp + libe * sp + litu * sp + nysy * sp + pist * sp + pivi * sp + ploc * sp + prav * sp + prse * sp + qual * sp + quco * sp + qufa * sp + qumi * sp + qupr * sp + quru * sp + quve * sp + rops * sp + saal * sp + saca * sp + tiam * sp + ulam * sp + ulru * sp + unk * sp + vipr * sp}
\end{Highlighting}
\end{Shaded}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{comp_bayes_lm_scbi}
\CommentTok{## Bayesian linear regression model parameters with a multivariate Normal}
\CommentTok{## likelihood. See ?comp_bayes_lm for details:}
\CommentTok{## }
\CommentTok{##   parameter_type           prior posterior}
\CommentTok{## 1 Inverse-Gamma on sigma^2 a_0   a_star   }
\CommentTok{## 2 Inverse-Gamma on sigma^2 b_0   b_star   }
\CommentTok{## 3 Multivariate t on beta   mu_0  mu_star  }
\CommentTok{## 4 Multivariate t on beta   V_0   V_star   }
\CommentTok{## }
\CommentTok{## Model formula:}
\CommentTok{## growth ~ sp + dbh + dbh * sp + acne * sp + acru * sp + amar * sp + astr}
\CommentTok{## * sp + caca * sp + caco * sp + cade * sp + cagl * sp + caovl * sp + cato}
\CommentTok{## * sp + ceca * sp + ceoc * sp + chvi * sp + cofl * sp + crpr * sp + crsp}
\CommentTok{## * sp + divi * sp + elum * sp + fagr * sp + fram * sp + frni * sp + frpe}
\CommentTok{## * sp + havi * sp + ilve * sp + juci * sp + juni * sp + libe * sp + litu}
\CommentTok{## * sp + nysy * sp + pist * sp + pivi * sp + ploc * sp + prav * sp + prse}
\CommentTok{## * sp + qual * sp + quco * sp + qufa * sp + qumi * sp + qupr * sp + quru}
\CommentTok{## * sp + quve * sp + rops * sp + saal * sp + saca * sp + tiam * sp + ulam}
\CommentTok{## * sp + ulru * sp + unk * sp + vipr * sp}
\end{Highlighting}
\end{Shaded}
